---
title: "My Shiny App"
author: "EA"
date: '2022-06-16'
output: ioslides_presentation
---

 
## About the App

This is Shiny App that plots the popularity of a user's first name over time. The babynames data set in R is used. 

 

## The Baby names Data set

### Description 

Full baby name data provided by the SSA. This includes all names used at least five times.The data set is a data frame with five variables: `year`, `sex`, `name`, `n` and `prop`.

`prop` is just `n` divided by the total number of applicants in the year. This means, proportions are of the people of that sex with that name born in that year.

*** 
**A preview of the babynames data set**
```{r, comment = ""}
library(babynames)
head(babynames)
```


## A plot of the name Richard over time

```{r, message = FALSE, echo = FALSE}
library(ggplot2)
library(dplyr)
babynames %>%
    filter(name == "Richard", sex == "M") %>%
    ggplot() + geom_line(mapping = aes(x = year, y = prop)) +
    labs(title = "Popularity of the name Richard")

```


